---
title: "Activity: Nuclear Reactors"
author: "Alvin Chen"
output: html_notebook
---

```{r}
library(tidyverse)

```

## Scrape the Data 

```{r}
#My code here....

#Scrape
library(rvest)

webpage <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"

table_list <- webpage %>%
  read_html(header = TRUE) %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

str(table_list)

japan_reactors <- table_list[[21]]

#examine
head(japan_reactors)
View(japan_reactors)

```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

The table is not quite tidy as whats upposed to be the first row is just added variables to the data set. The column headers are not clear to understand. There are some cases with missing values. 

## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here
#remove first row
japan_reactors <-
  japan_reactors[-1, ] 

#get rid of missing values
japan_reactors <- japan_reactors %>%
  select(where(~ any(. != "", na.rm = TRUE)))

#get rid of closed variable
japan_reactors <- 
  japan_reactors[, !(names(japan_reactors) %in% "Closed")]

#got rid of empty cells
japan_reactors <- japan_reactors %>%
  filter(Model != "" & Beginbuilding != "" & Commercialoperation != "")

#plot
ggplot(japan_reactors) +
  geom_tile(aes(x = `Capacity(MW)`, y = Beginbuilding)) +
  xlab("Net Generation Capacity") +
  ylab("Construction Date")

```
Observations: In looing at the plotted data, there seems to be a wide range of generation cpacity and no general trend throughtout the data. There are more reactors with lower capactity than there are that can hold more.

## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 
#scrape
library(rvest)

webpage <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"

table_list <- webpage %>%
  read_html(header = TRUE) %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

str(table_list)

china_reactors <- table_list[[10]]
View(china_reactors)

#get rid of first row
china_reactors <-
  china_reactors[-1, ] 

#get rid of missing data
china_reactors <- china_reactors %>%
  select(where(~ any(. != "", na.rm = TRUE)))

china_reactors <- china_reactors %>%
  filter(Beginbuilding != "" & Commercialoperation != "")

#merge china and japan
china_japan_reactors <-
  merge(china_reactors, japan_clean, all = TRUE)

#examine
View(china_japan_reactors)
```

Observations: China has more PWR type nuclear reactors than Japan. A lot of japan's reactors are under review or shut down, while china has mostly operational reactors and ones that are under construction.
## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#convert the dates to have the same format
japan_reactors$Beginbuilding <- 
  as.Date(japan_reactors$Beginbuilding, format = "%d %b %Y")
japan_reactors$Commercialoperation <- 
  as.Date(japan_reactors$Commercialoperation, format = "%d %b %Y")

#create new variable that uses the reactor name with its respective unite ID
japan_reactors$PlantID <- 
  paste(as.character(japan_reactors$Plantname), as.character(japan_reactors$UnitNo.), sep = " ")

#make a start and an end for plot points
japan_reactors <- japan_reactors %>%
  mutate(StartDate = as.Date(Beginbuilding),
         EndDate = as.Date(Commercialoperation))
  
#gets only the top half of the reactors to plot
top_half_reactors <-
  japan_reactors[1:(nrow(japan_reactors)/2), ]

head(top_half_reactors)

#plot
ggplot(top_half_reactors) +
  geom_segment(aes(x = StartDate, xend = EndDate, y = PlantID, yend = PlantID, size = Status, color = Type)) +
  scale_fill_hue(direction = 1) +
  theme_minimal() +
  xlab('operation') +
  ylab('reactorID')



```
Observations: From 1970-1995 Japan has more reacters compared to any time past 2000's. The majority of Japan's reactors are type BWR. And a lot of their reactors are shut down with others are under review.